\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2018-12-20 redaction/TC_new.tex
Nouvelle version après relecture

\title{\textsc{International Transport costs:\\New Findings from modeling additive costs}\thanks{We are grateful to Holger Görg, S\'{e}bastien Jean and Vincent Vicard for their insightful comments. The paper has greatly benefited from remarks from the participants at ETSG 17\textsuperscript{th} (Helsinki), DEGIT XXII (Paris), seminars at the universities of California-Irvine, Paris-Dauphine, Paris-I and Nancy and the Kiel Institute for the World Economy.
Any remaining errors are ours. This paper was partly funded by a university grant from Lille-I University. It features an online appendix containing additional results, available on the authors' websites.}}

@@

\begin{abstract}
This paper investigates the pattern of international transport costs over time, using information contained in the US imports flows from 1974 to 2013. First, we document the importance of the per-unit (additive) component of transport costs. We find that additive costs are quantitatively sizable, representing between one-third and one-half of overall transport costs. Second, we identify the respective roles of the reduction in ``pure'' transport costs and trade composition effects in the downward trend of international transport costs, in the same spirit as \cite{hummels2007}. Unlike him, we find that trade composition effects do not matter much and, when they do, they tend to amplify (rather than reduce) the decrease in pure transport costs. Importantly, this difference of results can be attributed to the new method of modeling the per-unit component of transport costs we offer. In both aspects, our results point to the importance of the additive component in accounting for international transport costs.
\end{abstract}

@@

In both aspects, our results point to the importance of the additive component in accounting for international transport costs.
In this respect, it contributes to the literature that challenges the dominant role of iceberg costs in international trade (even in the case of ice transport, see \citealp{bosker2018ice}).
As shown by \cite{alchian}, the relative price of two varieties of some goods will depend on the level of additive trade costs.
In this context, the relative demand for more expensive/higher-quality product goods increases with trade costs (``shipping the good apples out'').
This is consistent with the findings by \citet{hummels_skiba}, who estimate the elasticity of freight rates with respect to price to be well below unity.
Also, their estimates imply that doubling freight costs increases average free alongside ship (fas) export prices by 80\% to 141\%, consistent with high-quality goods being sold in markets with high freight costs.
Recent empirical studies based on micro-level data also provide strong empirical support for the role of additive costs (i.e. cost per unit exported) in international trade costs.
Based on a firm-product-level database of French exporters, \citet{martin2012} finds that firms charge higher unit values for exports to more remote countries, supporting the importance of additive costs.
Using transaction-level trade data from Colombia, \cite{Lashkaripour-2017b} estimates that the transport cost elasticity varies greatly across industries, with a value of 0.8 for the average industry, in contrast with the iceberg specification.\footnote{Beyond the positive aspect, several recent papers also point out the normative implications of additive trade costs. \citet{sorensen2014} extends \citet{melitz}'s seminal model of international trade by including additive trade costs, in addition to the ad-valorem component. A key analytical result is that the welfare gain from a reduction in trade barriers is higher for a decrease in additive costs than a decrease in ad-valorem costs, due to the alteration of relative prices in a heterogeneous-firms trade framework. This is confirmed by \cite{Irrazabal_2015}. While these results suggest that important welfare gains can be achieved by reducing additive trade costs, not much progress has been made in quantifying such gains. One potential reason is the lack of an empirical characterization of the additive component of trade costs (the one exception being \citealp{Irrazabal_2015}). One contribution of this paper is to fill that gap.}

@@

\begin{figure}[htbp]
\caption{Trend in estimated transport costs (yearly mean value)}
\label{fig:Trends_in_TC}
\begin{center}
\includegraphics[width=14cm, height=6.5cm]{Figure2_Trend_of_totalTC_bymode.pdf}
\end{center}
\end{figure}

\textbf{JH: ATTENTION!!! TYPO à changer dans la Figure 2 ? STILL HERE ? }

@@

\begin{figure}[htbp]
\caption{Characterizing the time trends: applying Hummel's (2007) method }
\label{fig:comp_effects_as_in_Hummels}
\begin{center}
\begin{tabular}{cc}
{\small (a) Ad-valorem air Freight} & {\small (b) Ad-valorem vessel Freight}\\
\multicolumn{2}{c}{{\small In percent of the export price}} \\
\includegraphics[width=2.5in, height=1.8in]{figure5_comme_hummels.pdf}
& \includegraphics[width=2.5in,height=1.8in]{figure6_comme_hummels.pdf} \\
{\small (c) Ad-valorem air Freight} & {\small (d) Ad-valorem vessel Freight}\\
\multicolumn{2}{c}{{\small As indices with reference value 100 in 1974} }\\
\includegraphics[width=2.5in, height=2in]{figure5_comme_hummels_base100.pdf}
& \includegraphics[width=2.5in,height=2in]{figure6_comme_hummels_base100.pdf} \\
\end{tabular}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\caption{Robustness to the separability assumption (year-to-year basis)}
\label{fig:robustesse_non_separe}
\begin{center}
\begin{tabular}{cc}
{\small (a) Air Freight} & {\small (b) Vessel Freight}\\
\includegraphics[width=2.5in, height=2in]{graph_robustesse_ns_mp_terme_A_air.pdf}
& \includegraphics[width=2.5in,height=2in]{graph_robustesse_ns_mp_terme_A_ves.pdf} \\
\includegraphics[width=2.5in, height=2in]{graph_robustesse_ns_mp_terme_I_air.pdf}
& \includegraphics[width=2.5in,height=2in]{graph_robustesse_ns_mp_terme_I_ves.pdf} \\

\end{tabular}
\end{center}
\end{figure}

@@

We now report the goodness-of-fit exercise (conducted by transport mode) at the 4-digit product classification level (for the selected years).
The results are reported in Tables \ref{tab:good_fit_air_rob} (for air) and \ref{tab:good_fit_ves_rob} (for vessel).
\begin{table}[htbp]
  \centering
  \caption{Air: Measures of goodness of fit, 4-digit level}
\begin{center}
\label{tab:good_fit_air_rob}%
%\vspace{0.5cm}
%\scalebox{0.97}{
  \footnotesize{
\begin{tabular}{l|cccccc}
\hline
\hline
      & \multicolumn{6}{c}{Year}              \\
      & \multicolumn{1}{c}{1974} & \multicolumn{1}{c}{1981} & \multicolumn{1}{c}{1989} & \multicolumn{1}{c}{2001} & \multicolumn{1}{c}{2009} & \multicolumn{1}{c}{2013}  \\
\hline
\textbf{R2} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &       &       &      \\
Model (a)& \multicolumn{1}{c}{0.48} & \multicolumn{1}{c}{0.49} & \multicolumn{1}{c}{0.50} & \multicolumn{1}{c}{0.50} & \multicolumn{1}{c}{0.45} & \multicolumn{1}{c}{0.35} \\
Model (b) & \multicolumn{1}{c}{0.63} & \multicolumn{1}{c}{0.66} & \multicolumn{1}{c}{0.65} & \multicolumn{1}{c}{0.66} & \multicolumn{1}{c}{0.54} & \multicolumn{1}{c}{0.45} \\
\textbf{SER} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &       & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}  \\
Model (a)& \multicolumn{1}{c}{0.8} & \multicolumn{1}{c}{0.9} & \multicolumn{1}{c}{0.83} &   0.87    & \multicolumn{1}{c}{0.88} & \multicolumn{1}{c}{0.93}  \\
Model (b) & \multicolumn{1}{c}{0.67} & \multicolumn{1}{c}{0.74} & \multicolumn{1}{c}{0.69} &  0.80     & \multicolumn{1}{c}{0.80} & \multicolumn{1}{c}{0.86}  \\
\textbf{Log-likelihood} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &       & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
Model (a) & \multicolumn{1}{c}{-17505.6} & \multicolumn{1}{c}{-21813.5} & \multicolumn{1}{c}{-30960.6} & \multicolumn{1}{c}{-44067.6} & \multicolumn{1}{c}{-49375.6} & \multicolumn{1}{c}{-53197.9}  \\
Model (b) & \multicolumn{1}{c}{-14895.8} & \multicolumn{1}{c}{-18589.9} & \multicolumn{1}{c}{-26553.5} & \multicolumn{1}{c}{-37297.9} & \multicolumn{1}{c}{-45747.6} & \multicolumn{1}{c}{-49899.1}  \\
\textbf{AIC criteria} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &       & \multicolumn{1}{c}{}  \\
Model (a)& \multicolumn{1}{c}{36243.1} & \multicolumn{1}{c}{44966.9} & \multicolumn{1}{c}{63417.1} & \multicolumn{1}{c}{89747.2} & \multicolumn{1}{c}{100317.13} & \multicolumn{1}{c}{107963.7} \\
Model (b) & \multicolumn{1}{c}{31873.6} & \multicolumn{1}{c}{39495.8} & \multicolumn{1}{c}{55777.1} & \multicolumn{1}{c}{77439.9} & \multicolumn{1}{c}{94059.1} & \multicolumn{1}{c}{102224.3}  \\
\textbf{Test LL} &       &       &       &       &       &       \\
2$\times$(ll(UR) -ll(R)) & \multicolumn{1}{c}{5219.5} & \multicolumn{1}{c}{6447.1} & \multicolumn{1}{c}{8814.1} & \multicolumn{1}{c}{13539.4} & \multicolumn{1}{c}{7256.0} & \multicolumn{1}{c}{6597.5}  \\
\# restrictions  & \multicolumn{1}{c}{640} & \multicolumn{1}{c}{698} & \multicolumn{1}{c}{778} & \multicolumn{1}{c}{833} & \multicolumn{1}{c}{824} & \multicolumn{1}{c}{818}  \\
p-value & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.000} \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{13cm}{ \vspace{7pt}\scriptsize{Notes: Model (a) = with only ad-valorem transport costs.
Model (b) = with additive \& ad-valorem
transport costs.
$R^{2}$ between the log of predicted ratio and the log of the observed ratio.
The number \# of restrictions is equal to the number of parameters estimated, i.e. the number of partner countries plus the number of products.}}}
\end{tabular}%
}
\end{center}
\end{table}%

\begin{table}[htbp]
  \centering
  \caption{Vessel: Measures of goodness of fit, 4-digit level}
\begin{center}
\label{tab:good_fit_ves_rob}%
  \footnotesize{
\begin{tabular}{l|cccccc}
\hline
\hline
      & \multicolumn{6}{c}{Year}                   \\
      & \multicolumn{1}{c}{1974} & \multicolumn{1}{c}{1981} & \multicolumn{1}{c}{1989} & \multicolumn{1}{c}{2001} & \multicolumn{1}{c}{2009} & \multicolumn{1}{c}{2013}  \\ \hline
\boldmath{}\textbf{R$^{2}$}\unboldmath{} &       &       &       &       &       &         \\
Term I only & 0.50  & 0.45  & \multicolumn{1}{c}{0.47} & \multicolumn{1}{c}{0.41} & \multicolumn{1}{c}{0.37} & \multicolumn{1}{c}{0.35} \\
Terms A \& I & 0.66  & 0.62  & \multicolumn{1}{c}{0.62} & \multicolumn{1}{c}{0.58} & \multicolumn{1}{c}{0.51} & \multicolumn{1}{c}{0.46} \\
\textbf{SER} &       &       & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
Model (a) &    0.58   &   0.64    & \multicolumn{1}{c}{0.61} & \multicolumn{1}{c}{0.0.72} & \multicolumn{1}{c}{0.79} & \multicolumn{1}{c}{0.82} \\
Model (b) &   0.48    &    0.53   & \multicolumn{1}{c}{0.51} & \multicolumn{1}{c}{0.61} & \multicolumn{1}{c}{0.69} & \multicolumn{1}{c}{0.75} \\
\textbf{Log-likelihood} &       &       & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
Model (a)& -16460.1 & -16951.6 & \multicolumn{1}{c}{-26771.4} & \multicolumn{1}{c}{-39008.3} & \multicolumn{1}{c}{-43888.9} & \multicolumn{1}{c}{-47161.6} \\
Model (b) & -12743.65 & -13546.9 & \multicolumn{1}{c}{-21752.8} & \multicolumn{1}{c}{-33281.0} & \multicolumn{1}{c}{-39078.9} & \multicolumn{1}{c}{-43399.2}  \\
\textbf{AIC criteria} &       &       & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
Model (a) & 34464.2 & 35491.2 & \multicolumn{1}{c}{55272.9} & \multicolumn{1}{c}{79800.7} & \multicolumn{1}{c}{89459.8} & \multicolumn{1}{c}{95987.2}\\
Model (b) & 28271.3 & 29877.8 & \multicolumn{1}{c}{46595.6} & \multicolumn{1}{c}{69743.9} & \multicolumn{1}{c}{81155.7} & \multicolumn{1}{c}{89692.4} \\
\textbf{Test LL} &       &       & & &  & \\
2$\times$(ll(UR) -ll(R)) & 12385.80 & 11226.8 & \multicolumn{1}{c}{17354.7} & \multicolumn{1}{c}{20113.5} & \multicolumn{1}{c}{16608.2} & \multicolumn{1}{c}{12589.6} \\
\# restrictions  & 797   & 814   & \multicolumn{1}{c}{881} & \multicolumn{1}{c}{910} & \multicolumn{1}{c}{886} & \multicolumn{1}{c}{874} \\
p-value & 0.000 & 0.000 & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{13cm}{ \vspace{7pt}\scriptsize{Notes: Model (a) = with only ad-valorem transport costs.
Model (b) = with additive \& ad-valorem
transport costs.
$R^{2}$ between the log of predicted ratio and the log of the observed ratio.
The number \# of restrictions is equal to the number of parameters estimated, i.e. the number of partner countries plus the number of products.}}}
\end{tabular}%
}
\end{center}
\end{table}%

>>>>

\title{\textsc{International Transport costs:\\New Findings from modeling additive costs}\thanks{We are grateful to Holger G\"{o}rg, S\'{e}bastien Jean and Vincent Vicard for their insightful comments. The paper has greatly benefited from remarks from the participants at ETSG 17\textsuperscript{th} (Helsinki), DEGIT XXII (Paris), seminars at the universities of California-Irvine, Paris-Dauphine, Paris-I and Nancy and the Kiel Institute for the World Economy.
Any remaining errors are ours. This paper was partly funded by a university grant from Lille-I University. It features an online appendix containing additional results, available on the authors' websites.}}

@@

\begin{abstract}
This paper investigates the pattern of international transport costs over time, using information contained in the US imports flows from 1974 to 2013. First, we document the importance of the per-unit component of transport costs. It represents between one-third and one-half of overall transport costs. Second, allowing for time-varying per-unit costs, we find that the downward trend in international transport costs comes from the reduction in “pure” transport costs over time, with trade composition effects playing a minor role. In both aspects, our results point to the importance of the additive component in accounting for international transport costs
\end{abstract}

@@

In both aspects, our results point to the importance of the additive component in accounting for international transport costs.
In this respect, it contributes to the literature that challenges the dominant role of iceberg costs in international trade (even in the case of ice transport, see \citealp{bosker2018ice}).
As shown by \cite{alchian}, the relative price of two varieties of some goods will depend on the level of additive trade costs.
In this context, the relative demand for more expensive/higher-quality product goods increases with trade costs (``shipping the good apples out'').
This is consistent with the findings by \citet{hummels_skiba}, who estimate the elasticity of freight rates with respect to price to be well below unity.
Also, their estimates imply that doubling freight costs increases average free alongside ship (FAS) export prices by 80\% to 141\%, consistent with high-quality goods being sold in markets with high freight costs.
Recent empirical studies based on micro-level data also provide strong empirical support for the role of additive costs (i.e. cost per unit exported) in international trade costs.
Based on a firm-product-level database of French exporters, \citet{martin2012} finds that firms charge higher unit values for exports to more remote countries, supporting the importance of additive costs.
Using transaction-level trade data from Colombia, \cite{Lashkaripour-2017b} estimates that the transport cost elasticity varies greatly across industries, with a value of 0.8 for the average industry, in contrast with the iceberg specification.\footnote{Beyond the positive aspect, several recent papers also point out the normative implications of additive trade costs. \citet{sorensen2014} extends \citet{melitz}'s seminal model of international trade by including additive trade costs, in addition to the ad-valorem component. A key analytical result is that the welfare gain from a reduction in trade barriers is higher for a decrease in additive costs than a decrease in ad-valorem costs, due to the alteration of relative prices in a heterogeneous-firms trade framework. This is confirmed by \cite{Irrazabal_2015}. While these results suggest that important welfare gains can be achieved by reducing additive trade costs, not much progress has been made in quantifying such gains. One potential reason is the lack of an empirical characterization of the additive component of trade costs (the one exception being \citealp{Irrazabal_2015}). One contribution of this paper is to fill that gap.}

@@

\begin{figure}[htbp]
\caption{Trend in estimated transport costs (yearly mean value)}
\label{fig:Trends_in_TC}
\begin{center}
\includegraphics[width=14cm, height=7cm]{Figure2_Trend_of_totalTC_bymode.pdf}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\caption{Characterizing the time trends: applying Hummel's (2007) method }
\label{fig:comp_effects_as_in_Hummels}
\begin{center}
\begin{tabular}{cc}
{\small (a) Ad-valorem air freight} & {\small (b) Ad-valorem vessel freight}\\
\multicolumn{2}{c}{{\small In percent of the export price}} \\
\includegraphics[width=2.5in, height=1.8in]{figure5_comme_hummels.pdf}
& \includegraphics[width=2.5in,height=1.8in]{figure6_comme_hummels.pdf} \\
{\small (c) Ad-valorem air freight} & {\small (d) Ad-valorem vessel freight}\\
\multicolumn{2}{c}{{\small As indices with reference value 100 in 1974} }\\
\includegraphics[width=2.5in, height=2in]{figure5_comme_hummels_base100.pdf}
& \includegraphics[width=2.5in,height=2in]{figure6_comme_hummels_base100.pdf} \\
\end{tabular}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\caption{Robustness to the separability assumption (year-to-year basis)}
\label{fig:robustesse_non_separe}
\begin{center}
\begin{tabular}{cc}
{\small (a) Air freight} & {\small (b) Vessel freight}\\
\includegraphics[width=3in, height=2in]{graph_robustesse_ns_mp_terme_A_air.pdf}
& \includegraphics[width=3in,height=2in]{graph_robustesse_ns_mp_terme_A_ves.pdf} \\
\includegraphics[width=3in, height=2in]{graph_robustesse_ns_mp_terme_I_air.pdf}
& \includegraphics[width=3in,height=2in]{graph_robustesse_ns_mp_terme_I_ves.pdf} \\

\end{tabular}
\end{center}
\begin{minipage} [c]  {5in} \scriptsize%
Notes: FE for (country, sector) fixed effects.
\end{minipage}
\end{figure}

@@

We now report the goodness-of-fit exercise (conducted by transport mode) at the 4-digit product classification level (for the selected years).
The results are reported in Tables \ref{tab:good_fit_air_rob} (for air) and \ref{tab:good_fit_ves_rob} (for vessel).
\begin{table}[htbp]
  \centering
  \caption{Air: Measures of goodness of fit, 4-digit level}
\begin{center}
\label{tab:good_fit_air_rob}%
%\vspace{0.5cm}
%\scalebox{0.97}{
  \footnotesize{
\begin{tabular}{l|cccccc}
\hline
\hline
      & \multicolumn{6}{c}{Year}              \\
      & \multicolumn{1}{c}{1974} & \multicolumn{1}{c}{1981} & \multicolumn{1}{c}{1989} & \multicolumn{1}{c}{2001} & \multicolumn{1}{c}{2009} & \multicolumn{1}{c}{2013}  \\
\hline
\multicolumn{7}{l}{\textbf{R$^2$}}      \\ \hline
Model (a)& \multicolumn{1}{c}{0.48} & \multicolumn{1}{c}{0.49} & \multicolumn{1}{c}{0.50} & \multicolumn{1}{c}{0.50} & \multicolumn{1}{c}{0.45} & \multicolumn{1}{c}{0.35} \\
Model (b) & \multicolumn{1}{c}{0.63} & \multicolumn{1}{c}{0.66} & \multicolumn{1}{c}{0.65} & \multicolumn{1}{c}{0.66} & \multicolumn{1}{c}{0.54} & \multicolumn{1}{c}{0.45} \\ \hline
\multicolumn{7}{l}{\textbf{SER} }  \\ \hline
Model (a)& \multicolumn{1}{c}{0.8} & \multicolumn{1}{c}{0.9} & \multicolumn{1}{c}{0.83} &   0.87    & \multicolumn{1}{c}{0.88} & \multicolumn{1}{c}{0.93}  \\
Model (b) & \multicolumn{1}{c}{0.67} & \multicolumn{1}{c}{0.74} & \multicolumn{1}{c}{0.69} &  0.80     & \multicolumn{1}{c}{0.80} & \multicolumn{1}{c}{0.86}  \\
\multicolumn{7}{l}{\textbf{Log-likelihood} } \\ \hline
Model (a) & \multicolumn{1}{c}{-17505.6} & \multicolumn{1}{c}{-21813.5} & \multicolumn{1}{c}{-30960.6} & \multicolumn{1}{c}{-44067.6} & \multicolumn{1}{c}{-49375.6} & \multicolumn{1}{c}{-53197.9}  \\
Model (b) & \multicolumn{1}{c}{-14895.8} & \multicolumn{1}{c}{-18589.9} & \multicolumn{1}{c}{-26553.5} & \multicolumn{1}{c}{-37297.9} & \multicolumn{1}{c}{-45747.6} & \multicolumn{1}{c}{-49899.1}  \\ \hline
\multicolumn{7}{l}{\textbf{AIC criteria} }  \\ \hline
Model (a)& \multicolumn{1}{c}{36243.1} & \multicolumn{1}{c}{44966.9} & \multicolumn{1}{c}{63417.1} & \multicolumn{1}{c}{89747.2} & \multicolumn{1}{c}{100317.13} & \multicolumn{1}{c}{107963.7} \\
Model (b) & \multicolumn{1}{c}{31873.6} & \multicolumn{1}{c}{39495.8} & \multicolumn{1}{c}{55777.1} & \multicolumn{1}{c}{77439.9} & \multicolumn{1}{c}{94059.1} & \multicolumn{1}{c}{102224.3}  \\ \hline
\multicolumn{7}{l}{\textbf{Test LL} }    \\ \hline
2$\times$(ll(UR) -ll(R)) & \multicolumn{1}{c}{5219.5} & \multicolumn{1}{c}{6447.1} & \multicolumn{1}{c}{8814.1} & \multicolumn{1}{c}{13539.4} & \multicolumn{1}{c}{7256.0} & \multicolumn{1}{c}{6597.5}  \\
\# restrictions  & \multicolumn{1}{c}{640} & \multicolumn{1}{c}{698} & \multicolumn{1}{c}{778} & \multicolumn{1}{c}{833} & \multicolumn{1}{c}{824} & \multicolumn{1}{c}{818}  \\
p-value & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.000} \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{13cm}{ \vspace{7pt}\scriptsize{Notes: Model (a) = with only ad-valorem transport costs.
Model (b) = with additive \& ad-valorem
transport costs.
$R^{2}$ between the log of predicted ratio and the log of the observed ratio.
The number \# of restrictions is equal to the number of parameters estimated, i.e. the number of partner countries plus the number of products.}}}
\end{tabular}%
}
\end{center}
\end{table}%

\begin{table}[htbp]
  \centering
  \caption{Vessel: Measures of goodness of fit, 4-digit level}
\begin{center}
\label{tab:good_fit_ves_rob}%
  \footnotesize{
\begin{tabular}{l|cccccc}
\hline
\hline
      & \multicolumn{6}{c}{Year}                   \\
      & \multicolumn{1}{c}{1974} & \multicolumn{1}{c}{1981} & \multicolumn{1}{c}{1989} & \multicolumn{1}{c}{2001} & \multicolumn{1}{c}{2009} & \multicolumn{1}{c}{2013}  \\ \hline
\multicolumn{7}{l}{\textbf{R$^{2}$}} \\ \hline
Term I only & 0.50  & 0.45  & \multicolumn{1}{c}{0.47} & \multicolumn{1}{c}{0.41} & \multicolumn{1}{c}{0.37} & \multicolumn{1}{c}{0.35} \\
Terms A \& I & 0.66  & 0.62  & \multicolumn{1}{c}{0.62} & \multicolumn{1}{c}{0.58} & \multicolumn{1}{c}{0.51} & \multicolumn{1}{c}{0.46} \\ \hline
\multicolumn{7}{l}{\textbf{SER} }\\ \hline
Model (a) &    0.58   &   0.64    & \multicolumn{1}{c}{0.61} & \multicolumn{1}{c}{0.0.72} & \multicolumn{1}{c}{0.79} & \multicolumn{1}{c}{0.82} \\
Model (b) &   0.48    &    0.53   & \multicolumn{1}{c}{0.51} & \multicolumn{1}{c}{0.61} & \multicolumn{1}{c}{0.69} & \multicolumn{1}{c}{0.75} \\ \hline
\multicolumn{7}{l}{\textbf{Log-likelihood} } \\ \hline
Model (a)& -16460.1 & -16951.6 & \multicolumn{1}{c}{-26771.4} & \multicolumn{1}{c}{-39008.3} & \multicolumn{1}{c}{-43888.9} & \multicolumn{1}{c}{-47161.6} \\
Model (b) & -12743.65 & -13546.9 & \multicolumn{1}{c}{-21752.8} & \multicolumn{1}{c}{-33281.0} & \multicolumn{1}{c}{-39078.9} & \multicolumn{1}{c}{-43399.2}  \\ \hline
\multicolumn{7}{l}{\textbf{AIC criteria} } \\ \hline
Model (a) & 34464.2 & 35491.2 & \multicolumn{1}{c}{55272.9} & \multicolumn{1}{c}{79800.7} & \multicolumn{1}{c}{89459.8} & \multicolumn{1}{c}{95987.2}\\
Model (b) & 28271.3 & 29877.8 & \multicolumn{1}{c}{46595.6} & \multicolumn{1}{c}{69743.9} & \multicolumn{1}{c}{81155.7} & \multicolumn{1}{c}{89692.4} \\ \hline
\multicolumn{7}{l}{\textbf{Test LL}} \\ \hline
2$\times$(ll(UR) -ll(R)) & 12385.80 & 11226.8 & \multicolumn{1}{c}{17354.7} & \multicolumn{1}{c}{20113.5} & \multicolumn{1}{c}{16608.2} & \multicolumn{1}{c}{12589.6} \\
\# restrictions  & 797   & 814   & \multicolumn{1}{c}{881} & \multicolumn{1}{c}{910} & \multicolumn{1}{c}{886} & \multicolumn{1}{c}{874} \\
p-value & 0.000 & 0.000 & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{13cm}{ \vspace{7pt}\scriptsize{Notes: Model (a) = with only ad-valorem transport costs.
Model (b) = with additive \& ad-valorem
transport costs.
$R^{2}$ between the log of predicted ratio and the log of the observed ratio.
The number \# of restrictions is equal to the number of parameters estimated, i.e. the number of partner countries plus the number of products.}}}
\end{tabular}%
}
\end{center}
\end{table}%
